Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-24 WSSSPE1_report/WSSSPE1_summary_report.tex
small changes

\section{Keynotes\scriptsize{\note{lead: Sou-Cheng (Terrya) Choi}, \todo{include what was presented and discussed}}} \label{sec:keynotes}

@@

\section{Developing and Supporting Software} \label{sec:devel}

\note{lead: Marcus Hanwell, contributors: Suresh Marru}

@@

\section{Policy} \label{sec:policy}

\note{lead: Colin Venters}

@@

\section{Communities} \label{sec:community}

\note{lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}

@@

\section{Case Studies} \label{sec:use-cases}
\note{lead: Ketan Maheshwari, contributors: Andy Terrel}

@@

\appendix
\section{List of attendees}

\note{lead: Shel Swenson}

>>>>

\section{Keynotes \note{lead: Sou-Cheng (Terrya) Choi} } \label{sec:keynotes}

@@

\section{Developing and Supporting Software \note{lead: Marcus Hanwell, contributors: Suresh Marru}} \label{sec:devel}

@@

\section{Policy \note{lead: Colin Venters}} \label{sec:policy}

@@

\section{Communities \note{lead: Matthew Turk, contributors: Nancy Wilkins-Diehr, Chris Mattmann, Suresh Marru, Frank L\"{o}ffler, Andy Terrel}} \label{sec:community}

@@

\section{Case Studies \note{lead: Ketan Maheshwari, contributors: Andy Terrel}} \label{sec:use-cases}

@@

\appendix
\section{List of attendees \note{lead: Shel Swenson}}
